Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System

### 2022-12-12 paper-kelompok/main.tex
repeatability gram fix

The wavelength precision and transmittance of the device are affected by several factors. 
The first factor is the consistency of the internal structure of the product.
During the implementation and testing process, it was shown that checking or opening the casing for each for each adjustment done for troubleshooting causes a shift in the component. 
Light pathway obscured by other components cause a reduction in the light intensity which pass through the sample.

From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produces a different level of precision. 
ITO glass should have a holder, for example, given a casing with a clamp. 
This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-spec.png}}
    \caption{The display of the result (left) and spectrum (right) page of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
    \caption{The display of the table (left) and plot (right) page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}

>>>>

The wavelength precision and transmittance of the device were affected by several factors. 
The first factor was the stability of the internal structure of the product.
During the implementation and testing process, it was observed that opening and adjusting the device's case for troubleshooting caused positional shifts of the components. 
Light pathway obscured by other components could cause light intensity reduction.

From several tests, the treatment of the ITO glass layer (which has been coated with silicon oil and parafilm) also produced a different level of precision. 
ITO glass should have a holder, for example, a case with a clamp. 
This way, the light path length is constant. Other than that, the droplet's shape, which tends to be convex at the top, can cause lensing effect\cite{b3}.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{lcd-spec.png}}
    \caption{The display of the result (left) and spectrum (right) page of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{lcd-conc.png}}
    \caption{The display of the table (left) and plot (right) page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}
